Data Preparation

### 2019-01-10 Data Preparation.Rmd
structure

### Course Manuals
####Extracting Full Text
(For this section we use:`corpus_manuals`-contains the pdfs of the course manuals for the year 2017-2018 (most recently, available))

>>>>

#### Course Manuals
#####Extracting Full Text
(For this section we use:`corpus_manuals`-contains the pdfs of the course manuals for the year 2017-2018 (most recently, available))
